Opportunities for improvement in the care of adult trauma patients arriving

### 2025-04-18 manuscript.Rmd
fixat lite diagram versioner

#ändra till flowchart
Table 3 - Sample characteristics showing missing data.
```{r sample-characteristics, echo=FALSE}
sample.characteristics.table
```
#slut

@@

@@

Table 5 - Sub-OFI, classified according to BE

@@

Table 6 - Sub-OFI, classified according to SBP

@@

Table 7 and 8 adjusted log
```{r Adjusted_log, echo=FALSE}
combined_tableBE
combined_tableSBP
```

>>>>

#ändra till flowchart

#slut

@@

Table 3

@@

Table 4 - Sub-OFI, classified according to BE

@@

Table 5 - Sub-OFI, classified according to SBP

@@

Table 6 adjusted log BE
```{r masterBE, echo=FALSE}
master_combined_table_stepBE
```

Table 7 adjusted log SBP
```{r masterSBP, echo=FALSE}
master_combined_table_stepSBP
```
